FinalManuscript_DISCS_UG

### 2018-09-26 parts/08_appendices_a_cryptosystems.tex
Added Dasgupta-Pal cryptosystem to appendix

\subsection{Homomorphic properties}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1)g^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
  \end{align*}
\end{description}
In order to implement some image operations covered in this study, we require the exponentiation of ciphertexts to integer powers, i.e. we require a function $f$ so that
\begin{align*}
	D(f(E(m))) = m^k\bmod n
\end{align*}
for any plaintext $m \in \mathbb{Z}_n$, and positive integer $k$.

This is trivially feasible if $m^2 \bmod n$ and $E(m^2 \bmod n)$ are known, since one can use the following equation to raise $m$ to any positive integer power.
\begin{align*}
	D(E(m^k)^(m^2 \bmod n)\bmod n^2)= m^{k+2}\bmod n
\end{align*}

@@

\section{The Benaloh cryptosystem}
The Benaloh cryptosystem, initially proposed by Josh Benaloh in \cite{benaloh_dense_1994}, allows for the encryption of integers in $\mathbb{Z}_r$ for some odd integer $r$. We present here a corrected version by Fousse, et al. \cite{fousse_benalohs_2010} which corrects an error in the key generation algorithm which prevents accurate decryption in some cases.

@@

>>>>

\subsection{Homomorphic properties}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
  \end{align*}
\end{description}
In order to implement some image operations covered in this study, we require the exponentiation of ciphertexts to integer powers, i.e. we require a function $f$ so that
\begin{align*}
	D(f(E(m))) = m^k\bmod n
\end{align*}
for any plaintext $m \in \mathbb{Z}_n$, and positive integer $k$.

This is trivially feasible if $m^2 \bmod n$ and $E(m^2 \bmod n)$ are known, since one can use the following equation to raise $m$ to any positive integer power.
\begin{align*}
	D(E(m^k)^{m^2 \bmod n}\bmod n^2) &= m^2m^k\bmod n \\
	&= m^{k+2}\bmod n
\end{align*}

@@

\section{The Benaloh cryptosystem}
The Benaloh cryptosystem, initially proposed by Josh Benaloh in \cite{benaloh_dense_1994}, allows for the encryption of integers in $\mathbb{Z}_r$ for some odd integer $r$. It relies on the hardness of the \textit{discrete logarithm problem}. We present here a corrected version by Fousse, et al. \cite{fousse_benalohs_2010} which corrects an error in the key generation algorithm which prevents accurate decryption in some cases.

@@

\section{Dasgupta-Pal cryptosystem}
The Dasgupta-Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S. K. Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts. We begin our presentation of the Dasgupta-Pal cryptosystem with the following definition.

Given a message $m \in \mathbb{n}$, we denote
\begin{align*}
		m_p(x) = a_0 + a_1x + a_2x^2 + \cdots + a_kx^k
\end{align*}
where $a_ka_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.
\subsection{Key generation, encryption and decryption algorithms}
Let $\ell$ denote the security parameter of the cryptosystem.
Let $S_k$ be a prime number with $\ell$ bits.
Choose a random even integer $z$ of length $\log_2{\ell}$.

Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.

The scheme defines the encryption algorithm for a message $m \in \mathbb{Z}_n$ as follows:
\begin{align*}
	E(m) = y(x) + S_k\times d(x)
\end{align*}
where
$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.

Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
\begin{align*}
	m_p(x) = c(x) \bmod S_k \bmod 2
\end{align*}
Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$

As a fully homomorphic cryptosystem, homomorphic operations on ciphertext introduce noise which may interfere with decryption.
To eliminate noise from a polynomial ciphertext, the following refresh function is used.
\begin{align*}
	R(c(x)) = c(x) \bmod R_k
\end{align*}

\subsection{Homomorphic properties}
It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta-Pal cryptosystem.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1) + E(m_2))= m_1+m_2 & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1) \times E(m_2))= m_1 \times m_2 & \text{ (used for binary multiplication)}
  \end{align*}
\end{description}
